Verifying Demonstrations

### 2018-03-15 paper/protocol.tex
Starts writing the protocol details

\NewCryptoScheme{\PRIVOscheme}{PRIVO}
\NewAlgorithm{\PRIVOsetup}{\PRIVOscheme.\!Setup}
\NewAlgorithm{\PRIVOjoin}{\PRIVOscheme.\!Join}
\NewAlgorithm{\PRIVOparticipate}{\PRIVOscheme.\!Participate}
\NewAlgorithm{\PRIVOsubmit}{\PRIVOscheme.\!Submit}

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
The protocol consists of four phases: the setup, join, participation and 
submission phases.
We have an identification authority \(\ID\), an organizer Oscar, \(\O\), a 
protester Alice (\(\A\)) and a witness Bob \(\B\).

\NewCryptoEntity{\ID}{ID}

\emph{Setup.}
During the setup phase, we set up the needed keys.

>>>>

\NewCryptoScheme{\PRIVOscheme}{PRIVO}
\NewAlgorithm{\PRIVOsetup}{\PRIVOscheme.\!Setup}
\NewAlgorithm{\PRIVOreg}{\PRIVOscheme.\!Register}
\NewAlgorithm{\PRIVOjoin}{\PRIVOscheme.\!Join}
\NewAlgorithm{\PRIVOparticipate}{\PRIVOscheme.\!Participate}
\NewAlgorithm{\PRIVOsubmit}{\PRIVOscheme.\!Submit}

\NewCryptoEntity{\Alice}{A}
\NewCryptoEntity{\Bob}{B}
\NewCryptoEntity{\Carol}{C}

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
The protocol consists of four phases: the setup, join, participation and 
submission phases.
We have several roles.
We have \iac{CA} who is responsible for a one-to-one mapping between a person's 
identity and a cryptographic key.
We have the protesters Alice (\(\Alice\)), Bob (\(\Bob\)) and Carol (\(\Carol\)) 
who want to participate in a given protest.

\emph{Setup: \((spk, ssk)\gets \PRIVOsetup\).}
The setup phase is for the \ac{CA} to set up all the needed keys.
The \ac{CA} starts by generating a service public-private key-pair \((spk, 
  ssk)\) by the following.
\(\gets \PRIVOsetup[1^\lambda]\), where \(\lambda\) is the security parameter, 
and then publishes \(spk\).
\begin{algorithmic}
  \Function{\PRIVOsetup}{$1^\lambda$}
    \State{$spk\gets (g, G, q, \dots)$}
    \State{$ssk\gets (g, G, q, \dots)$}
    \State{\Return{$(spk, ssk)$}}
  \EndFunction
\end{algorithmic}
